Automatic Visual Inference for Linear Regression

### 2022-03-16 Milestone_presentation_1/Milestone_presentation_1/Milestone_presentation_1.Rmd
add first glm

@@

.caption[
Fig. 13: _Quasibinomial GLM for estimated power for different number of evaluations._ 
]]

>>>>

#### The power of each lineup from one to five evaluations is estimated.

#### The estimated power is further used in fitting a **quasi-binomial generalized linear model** with natural logarithm of effect size as the only regressor.

@@

.caption[
Fig. 13: _Quasibinomial GLM for estimated power for different number of evaluations. The left plot is for the cubic model, the right plot is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]
